Response to Reviewers $Rev^1$

### 2020-03-17 ICT_Frontiers_rev202001_reply.tex
update

				\item The idea of 'simulation'. This is a more minor point but I would appreciate if the authors could be clearer on this. It is arguable whether or not consciousness simulates anything (e.g. see Hoffman's interface theory); and some of the assertions the authors make re simulation seem unfounded anyways. But it could be that they mean something different or subtle (that consciousness is linked to or represents or etc the environment)\todo{I don't understand this question well}

>>>>

				\item The idea of 'simulation'. This is a more minor point but I would appreciate if the authors could be clearer on this. It is arguable whether or not consciousness simulates anything (e.g. see Hoffman's interface theory); and some of the assertions the authors make re simulation seem unfounded anyways. But it could be that they mean something different or subtle (that consciousness is linked to or represents or etc the environment)
